---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggjournals

<!-- badges: start -->
<!-- badges: end -->

The `ggjournals` package provides custom ggplot2 themes and color palettes for creating plots that adhere to the style guidelines of various journals, including BMJ, The Lancet, NEJM, and JAMA.

## Installation

You can install the package from GitHub using:

``` r
remotes::install_github("huichen99/ggjournals")
```

## Example

### Lancet Theme

Similarly, you can use the Lancet theme:

```{r example_lancet}
library(ggjournals)
library(ggplot2)

ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  theme_lancet()
```

### NEJM Theme

```{r example_nejm}
library(ggjournals)
library(ggplot2)

ggplot(mpg, aes(x = class, y = hwy)) +
  geom_boxplot() +
  theme_nejm()
```

### JAMA Theme

```{r example_jama}
library(ggjournals)
library(ggplot2)

ggplot(mpg, aes(x = class, y = hwy)) +
  geom_boxplot() +
  theme_jama()
```

### BMJ Theme

To use the BMJ theme, simply add theme_bmj() to your ggplot2 plot:

```{r example_bmj}
library(ggjournals)
library(ggplot2)

ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  theme_bmj()
```

<!-- 
You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. 
-->
